Understanding Structure and Selectivity in Nanostructured Lyotropic Liquid Crystal Membranes using Molecular Simulations

### 2020-04-30 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Formatted for JPCB with slight mods to intro
Cover letter for JPCB
moved things to SI

\externaldocument[M-]{Final_Draft}

@@

\title{Supplemental Material: Capturing Subdiffusive Solute Dynamics and 
Predicting Selectivity in Nanoscale Pores with Time Series Modeling.}
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

@@

  \begin{figure}[h]
  \centering
  % /figures/distributions_sfbm.py
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_GCL.pdf}
  \caption{}\label{fig:GCL_hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{GCL_powerlaw.pdf}
  \caption{}\label{fig:GCL_powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{GCL_hop_acf.pdf}
  \caption{}\label{fig:GCL_hop_acf}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_ACH.pdf}
  \caption{}\label{fig:ACH_hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{ACH_powerlaw.pdf}
  \caption{}\label{fig:ACH_powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{ACH_hop_acf.pdf}
  \caption{}\label{fig:ACH_hop_acf}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_MET.pdf}
  \caption{}\label{fig:MET_hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{MET_powerlaw.pdf}
  \caption{}\label{fig:MET_powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{MET_hop_acf.pdf}
  \caption{}\label{fig:MET_hop_acf}
  \end{subfigure}
  \caption{Hop length distributions, dwell time distributions and hop autocorrelation functions
  respectively for ethylene glycol (a-c), acetic acid (d-f) and methanol (g-i).
  See Section~\ref{M-section:AD_parameterization} of the main text for a more detailed discussion.
  }\label{fig:anticorrelated_hops}
  \end{figure}

@@

  We evaluated the predictive capabilities of the AD modeling approach by training
  the model parameters on the first half of the equilibrated MD trajectory data and
  then comparing the MSD calculated from AD model realizations to the MSD calculated
  from the second half of the equilibrated MD trajectory data. This metric is
  only meaningful if the ensemble of solute trajectories is stationary. In 
  Figure~\ref{fig:msd_comparison}, we show that urea and acetic acid show acceptable
  stationary behavior while methanol and ethylene glycol do not.

@@

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{1mode_msd_comparison_URE_train_front.pdf}
  \caption{Urea (1 mode)}\label{fig:1mode_msd_comparison_URE_train_front}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{2mode_msd_comparison_URE_train_front.pdf}
  \caption{Urea (2 modes)}\label{fig:2mode_msd_comparison_URE_train_front}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{1mode_msd_comparison_ACH_train_front.pdf}
  \caption{Acetic acid (1 mode)}\label{fig:1mode_msd_comparison_ACH_train_front}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{2mode_msd_comparison_ACH_train_front.pdf}
  \caption{Acetic acid (2 modes)}\label{fig:2mode_msd_comparison_ACH_train_front}
  \end{subfigure} 
  \caption{In most cases, when using power laws with exponential cut-offs 
  (sFBMcut and sFLMcut), the MSD curves predicted by the AD model trained on 
  the first half of the equilibrated data lie within the 1$\sigma$ confidence
  intervals of the MD MSD curves generated from the second half of the equilibrated
  solute data. The models which use pure power laws systematically under-predict
  the MD MSD curves. Over- and under-estimated curvature of the of urea and acetic acid's 
  MSD curves respectively causes the magnitude of urea's predicted MSDs to be 
  under-predicted at long timescales and those of acetic acid to be under-predicted
  at short timescales. Note that the sFBMcut and sFLMcut models are the same as 
  those in the main text.}\label{fig:train_test}
  \end{figure}

@@

  \newpage
  \section{Table of MSDDM parameters}\label{section:msddm_params}

>>>>

\externaldocument[M-]{ms}

@@

\title{Supporting Information: Capturing Subdiffusive Solute Dynamics and 
Predicting Selectivity in Nanoscale Pores with Time Series Modeling.}
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

  \section{Mean Squared Displacement}\label{section:msd}

  In this study, we primarily use the MSD as a tool for characterizing the average
  dynamic behavior of solute trajectories. Rather than using them to calculate 
  diffusion constants or to relate our simulations to experimental measurements, we
  compare MSDs calculated from MD simulations to those generated from our models 
  in order to validate those models. Therefore, it is only important that we use a
  consistent definition for calculating the MSD between modeled trajectories and
  directly observed MD trajectories.

  One can measure MSD in two ways. The ensemble averaged MSD measures 
  displacements with respect to a particle's initial position:
  \begin{equation}
  \langle z^2(t) \rangle = \langle z(t) - z(0) \rangle^2
  \label{eqn:ensemble_msd}
  \end{equation}
  Fits to the ensemble averaged MSD will always reproduce the form of 
  Equation~\ref{M-eqn:msd_form} of the main text. The time-averaged MSD measures all observed 
  displacements over time lag $\tau$: 
  \begin{equation}
  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
  \label{eqn:tamsd}
  \end{equation}
  where T is the length of the trajectory.

  The time averaged and ensemble averaged MSDs will give identical results 
  unless a system displays non-ergodic behavior. For a pure CTRW, the power 
  law distribution of trapping times leads to weak ergodicity breaking.
  In this case, the time-averaged MSD is linear while the ensemble averaged
  MSD has the form of Equation~\ref{M-eqn:msd_form} of the main text.~\cite{meroz_toolbox_2015} With
  power law trapping behavior, the time between hops diverges so there is no 
  characteristic measurement time scale of solute motion. In fact, as measurement 
  time increases, the average MSD of a CTRW tends to decrease, a phenomenon called
  aging, because trajectories with trapping times on the order of the measurement 
  time get incorporated into the calculation.~\cite{bel_weak_2005}

  We chose to use just the time-averaged MSD to compare MD trajectories with
  modeled trajectories, because, compared to the ensemble average, it is a more
  statistically robust measure of the average distance a solute travels over
  time. The ensemble MSD of only 24 solute trajectories would have much higher
  uncertainties.

@@

  \begin{figure}[h]
  \centering
  % /figures/distributions_sfbm.py
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_URE.pdf}
  \caption{}\label{fig:hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{URE_powerlaw.pdf}
  \caption{}\label{fig:powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{URE_hop_acf.pdf}
  \caption{}\label{fig:hop_acf}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_GCL.pdf}
  \caption{}\label{fig:GCL_hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{GCL_powerlaw.pdf}
  \caption{}\label{fig:GCL_powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{GCL_hop_acf.pdf}
  \caption{}\label{fig:GCL_hop_acf}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_ACH.pdf}
  \caption{}\label{fig:ACH_hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{ACH_powerlaw.pdf}
  \caption{}\label{fig:ACH_powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{ACH_hop_acf.pdf}
  \caption{}\label{fig:ACH_hop_acf}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_MET.pdf}
  \caption{}\label{fig:MET_hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{MET_powerlaw.pdf}
  \caption{}\label{fig:MET_powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{MET_hop_acf.pdf}
  \caption{}\label{fig:MET_hop_acf}
  \end{subfigure}
  \caption{Hop length distributions, dwell time distributions and hop autocorrelation functions
  respectively for urea (a-c), ethylene glycol (d-f), acetic acid (g-i), and methanol (j-l).
  Using urea as an example, (a) the distribution of hop lengths can be fit by a Gaussian in
  addition to a more general L\'evy stable distribution, though the L\'evy stable distribution
  does a better job of capturing the heavier tails and increased density near 0. We explore
  models fit to both distributions, as Gaussian hops are more convenient to model. (b) The 
  distribution of dwell times is fit well by a power law but it over-estimates the probability
  density at long dwell times. A power law truncated with an exponential cut-off better
  describes the probability of long dwell times in our simulations. (c) The hops are negatively
  correlated to their previous hop. In combination, (a) -- (c) support modeling solutes as either
  subordinated fractional Brownian or L\'evy motion.
  }\label{fig:anticorrelated_hops}
  \end{figure}

@@

  We observe that in some cases, solute trajectories extracted from our MD
  simulations display non-stationary behavior. We defined the perceived
  equilibration time point for each solute based on the time at which the
  number of solutes inside the pores and tails stabilized
  (Figure~\ref{fig:equilibration}). With this definition, we observe
  evidence of non-stationary solute behavior after the perceived equilibration
  point, on the $\mu$s timescale.

%  In Table~\ref{table:stationarity}, we compare
%  the MSD of the solutes calculated using trajectory data from the first and
%  second halves of the ``equilibrated" simulation time. Ethylene glycol and
%  methanol show considerable differences between the MSDs of the two halves.
%  Urea and acetic acid appear to demonstrate satisfactory stationarity. The
%  shapes of urea and acetic acid's MSD curves are also very similar (see
%  Figure~\ref{S-fig:msd_comparison} of the Supporting Information).

% BJC: This table summarizes the main text
%  \begin{table}[h]
%  \centering
%  \begin{tabular}{|c|c|c|}
%  \hline
%  \multirow{2}{*}{Residue} & \multicolumn{2}{c|}{MSD}            \\\cline{2-3}
%                           & First Half       & Second Half      \\\hline
%  urea                     & 0.31 (0.23, 0.40)& 0.35 (0.28, 0.43)\\\hline
%  ethylene glycol          & 3.11 (2.06, 4.25)& 1.03 (0.76, 1.29)\\\hline
%  methanol                 & 2.24 (1.61, 2.92)& 1.06 (0.77, 1.39)\\\hline
%  acetic acid              & 1.58 (1.11, 2.03)& 1.43 (1.10, 1.73)\\\hline
%
%  \end{tabular}
%  \caption{In order to be considered stationary, the MSD of the ensemble of
%	  solute trajectories should be the same independent of the portion of
%	  equilibrated trajectory that is analyzed. The MSD values in this
%	  table are averages taken after a 500 ns time lag, calculated
%	  independently from the first and second halves of the equilibrated
%	  solute trajectories. Urea and acetic acid both appear to satisfy the
%	  stationarity criteria, while ethylene glycol and methanol show
%	  significantly smaller MSDs when calculated from the second half of
%	  the equilibrated trajectories.}\label{table:stationarity}
%  \end{table}

  %We evaluated the predictive capabilities of the AD modeling approach by training
  We trained
  the model parameters on the first half of the equilibrated MD trajectory data and
  then compared the MSD calculated from AD model realizations to the MSD calculated
  from the second half of the equilibrated MD trajectory data. This metric is
  only meaningful if the ensemble of solute trajectories is stationary. In 
  Figure~\ref{fig:msd_comparison}, we show that urea and acetic acid show acceptable
  stationary behavior while methanol and ethylene glycol do not.

@@

  This brief analysis suggests that we may be operating on the border of the
  minimum amount of data required to accurately parameterize AD approach
  models. Working with only half of the data we collected ($\sim$ 2 $\mu$s
  post-equilibration) may not always be sufficient for extracting reliable
  parameter estimates. Therefore, in the main text, we employ parameters fit
  to the entire equilibrated portion of the solute trajectories. Even doubling
  the data might not be good enough for molecules with statistical 
  non-stationarity, meaning the predictive and interpretive power of the time
  series modeling applied to these trajectories will be lower.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{1mode_msd_comparison_URE_train_front.pdf}
  \caption{Urea (1 mode)}\label{fig:1mode_msd_comparison_URE_train_front}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{2mode_msd_comparison_URE_train_front.pdf}
  \caption{Urea (2 modes)}\label{fig:2mode_msd_comparison_URE_train_front}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{1mode_msd_comparison_ACH_train_front.pdf}
  \caption{Acetic acid (1 mode)}\label{fig:1mode_msd_comparison_ACH_train_front}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{2mode_msd_comparison_ACH_train_front.pdf}
  \caption{Acetic acid (2 modes)}\label{fig:2mode_msd_comparison_ACH_train_front}
  \end{subfigure} 
  \caption{In most cases, when using power laws with exponential cut-offs 
  (sFBMcut and sFLMcut), the MSD curves predicted by the AD model trained on 
  the first half of the equilibrated data lie within the 1$\sigma$ confidence
  intervals of the MD MSD curves generated from the second half of the equilibrated
  solute data. Over- and under-estimated curvature of the of urea and acetic acid's 
  MSD curves respectively causes the magnitude of urea's predicted MSDs to be 
  under-predicted at long timescales and those of acetic acid to be under-predicted
  at short timescales. The models which use pure power laws systematically under-predict
  the MD MSD curves. 
  % Note that the sFBMcut and sFLMcut models are the same as those in the main text.
  }\label{fig:train_test}
  \end{figure}

@@

  \newpage
  \section{MSDDM parameters}\label{section:msddm_params}

  We observe correlated emissions drawn from L\'evy stable distributions. The
  deviation of the emission distributions from Gaussian behavior is far more
  pronounced than that seen in the hop length distributions of the AD model.
  (see Figure~\ref{fig:gaussian_levy_comparison}) We therefore did not consider
  the Gaussian case for the MSDDM. The correlation structure between hops is 
  consistent with that of FLM (Figure~\ref{fig:msddm_acf}).

  \begin{figure}
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison.pdf}
  \caption{}\label{fig:gaussian_levy_comparison}
  \end{subfigure}
  % /figures/msddm_acf.py
  \begin{subfigure}{0.42\textwidth}
  \includegraphics[width=\textwidth]{msddm_acf.pdf}
  \caption{}\label{fig:msddm_acf}
  \end{subfigure}
  \caption{(a) The emission distributions of hop lengths are non-Gaussian and
	  heavy-tailed. Shown here is the emission distribution for transitions
	  between states. The maximum likelihood Gaussian fit severely
	  underestimates the empirical density of hops near and far from zero
	  while overestimating the density of hops at intermediate values. (b)
	  Jumps drawn from the transition distribution are negatively
	  correlated to each other. The normalized version of
	  Equation~\ref{M-eqn:flm_autocovariance} fits well to the data
	  suggesting FLM is an appropriate way to model jumps.}
	  \label{fig:msddm_emissions}
  \end{figure}

### 2020-04-30 Ben_Manuscripts/stochastic_transport/cover_letter_JCTC.tex
moved things to SI

	We are submitting ``\ManuscriptTitle'' by Benjamin J. Coscia
        and Michael R.  Shirts, for consideration for publication as
        an Article in the Journal of Chemical Theory and
        Computation. We expect this work to be of significant interest
        to researchers who study complex transport at the molecular
        level, as it describes important new approaches for estimating long
        time scale behavior and bulk transport behavior from shorter
        molecular trajectories exhibiting anomalous diffusion rather
        than Brownian motion. Please note that this article has been
        uploaded to arXiv with differences only in formatting:
        \href{https://arxiv.org/abs/2004.07905}{https://arxiv.org/abs/2004.07905}. \\

>>>>

	We are submitting ``\ManuscriptTitle'' by Benjamin J. Coscia
        and Michael R.  Shirts, for consideration for publication as
        an Article in the Journal of Chemical Theory and
        Computation. We expect this work to be of significant interest
        to researchers who study complex transport at the molecular
        level, as it describes important new approaches for estimating long
        time scale behavior and bulk transport behavior from shorter
        molecular trajectories exhibiting anomalous diffusion rather
        than Brownian motion. Please note that the content of this article
        %BJC: see if you agree with these changes
        has been uploaded to arXiv: \href{https://arxiv.org/abs/2004.07905}{https://arxiv.org/abs/2004.07905}.
        For submission to JCTC, we have made minor changes to the introduction,
        abstract and conclusion in order to make it more suited for readers of 
        the journal. We also made efforts to shorten the manuscript by moving 
        certain discussions and figures to the supporting information. \\

### 2020-04-30 Ben_Manuscripts/thesis/intro.tex
moved things to SI

  Municipal waste-waters are rich in carbon, nitrogen and phosphorus-containing 
  compounds.~\cite{romero_raw_2013} The recovery of such products, which can be 
  achieved using selective membranes, has numerous potential uses.\cite{sales_resource_2015}
  For example, nitrogen and phosphorus recovery can help sustain fertilizer 
  production which will help meet global food demand as population continues
  to increase.\cite{xie_membrane-based_2016}

>>>>

  Municipal waste-waters are rich in carbon, nitrogen and phosphorus-containing 
  compounds. The recovery of such products, which can be 
  achieved using selective membranes, has numerous potential uses.\cite{romero_raw_2013,sales_resource_2015}
  For example, nitrogen and phosphorus recovery can help sustain fertilizer 
  production which will help meet global food demand as population continues
  to increase.\cite{xie_membrane-based_2016}

### 2020-04-30 Ben_Manuscripts/thesis/stochastic_transport.tex
moved things to SI

  Three well-known classes of behavior leading to anomalous subdiffusion are
  continuous time random walks (CTRWs), fractional Brownian motion (FBM) and
  random walks on fractals (RWFs).\cite{meroz_toolbox_2015} These types of
  motion are frequently used alone or in combination to describe single
  particle trajectories.~\cite{morrin_three_2018,metzler_anomalous_2014} A CTRW
  is characterized by a distribution of hop lengths and dwell times, where
  trajectories consist of sequential independent random draws from each
  distribution.\cite{montroll_random_1965} FBM is common in crowded,
  viscoelastic environments where each jump comes from a Gaussian distribution
  but is anti-correlated to its previous
  steps.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
  An RWF is imposed by a system's geometry. Systems with tortuous pathways and
  dead ends cause anti-correlated
  motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}

>>>>

  Three well-known classes of behavior leading to anomalous subdiffusion are
  continuous time random walks (CTRWs), fractional Brownian motion (FBM) and
  random walks on fractals (RWFs). These types of
  motion are frequently used alone or in combination to describe single
  particle trajectories.~\cite{meroz_toolbox_2015,metzler_anomalous_2014,morrin_three_2018} A CTRW
  is characterized by a distribution of hop lengths and dwell times, where
  trajectories consist of sequential independent random draws from each
  distribution.\cite{montroll_random_1965} FBM is common in crowded,
  viscoelastic environments where each jump comes from a Gaussian distribution
  but is anti-correlated to its previous
  steps.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
  An RWF is imposed by a system's geometry. Systems with tortuous pathways and
  dead ends cause anti-correlated
  motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}

### 2020-04-30 Ben_Manuscripts/thesis/thesis.tex
spell checking and mod to usage of subdiffusion
moved things to SI

\usepackage{amssymb}		% to get all AMS symbols
\usepackage{graphicx}		% to insert figures
\usepackage{hyperref}		% PDF hyperreferences??
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{textcomp} % gets rid of \perthousand and \micro warnings that come from gensymb
\usepackage{gensymb}
\usepackage{subcaption}
\usepackage{tcolorbox}
\usepackage[export]{adjustbox}
\usepackage{listings}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{booktabs}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{diagbox}
\usepackage{array}

@@

\reader{Prof. Richard Noble}		%  2nd person to sign thesis
\readerThree{Prof. Douglas Gin}		%  3rd person to sign thesis
\readerFour{Prof. Matthew Glaser}
\readerFive{Prof. Robert Davis}

@@

  Periodic, nanostructured porous polymer membranes made from the cross-linked
  inverted hexagonal phase of self-assembled lyotropic liquid crystals (LLCs) are
  a promising class of materials for selective separations. There is a wide 
  design space available for liquid crystal monomer design which may allow one to
  tailor solute interactions within the membrane pores. Our currrent
  understanding of these membrane is based primarily on experimental measurements
  and macroscopic modeling which limits our insight and ability to design them 
  for specific applications.

@@

  In order to connect these microscopic chemically-dependent solute motions to
  macroscopic membrane performance, I develop three different stochastic models 
  of varying complexity.  
  First, using anomalous diffusion theory, we show how solute dynamics can be
  modeled as a fractional diffusion process subordinate to a continuous time
  random walk. We parameterize the distribution of dwell times, hop lengths between
  dwells and correlation between hops. Next, we generalize Markov state models, treating
  the configurational states of the system as a Markov process where each state has 
  distinct transport properties. Finally apply the infinite hidden Markov model, 
  an approach capable of automatically distinguishing and parameterizing an unknown 
  number of hidden dynamical modes in multidimensional solute time series. This model
  offers a flexibile approach to modeling solute motion and helps us to uncover 
  mechanisms with minimal human effort.

@@

% \LoFisShort	% use this only for 1-page Table of Figures
\emptyLoF	% use this if there is no List of Figures

% \LoTisShort	% use this only for 1-page Table of Tables
\emptyLoT	% use this if there is no List of Tables

>>>>

\usepackage{amssymb}		% to get all AMS symbols
\usepackage{graphicx}		% to insert figures
%\usepackage{hyperref}		% PDF hyperreferences??
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{textcomp} % gets rid of \perthousand and \micro warnings that come from gensymb
\usepackage{gensymb}
\usepackage{subcaption}
\usepackage{tcolorbox}
\usepackage[export]{adjustbox}
\usepackage{listings}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{booktabs}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{diagbox}
\usepackage{array}

@@

\reader{Prof. Matthew Glaser}

@@

  Periodic, nanostructured porous polymer membranes made from the cross-linked
  inverted hexagonal phase of self-assembled lyotropic liquid crystals (LLCs) are
  a promising class of materials for selective separations. There is a wide 
  design space available for liquid crystal monomer design which may allow one to
  tailor solute interactions within the membrane pores. Our current
  understanding of these membranes is based primarily on experimental measurements
  and macroscopic modeling which limits our insight and ability to design them 
  for specific applications.

@@

  In order to connect these microscopic chemically-dependent solute motions to
  macroscopic membrane performance, I develop three different stochastic models 
  of varying complexity.  
  First, using anomalous diffusion theory, we show how solute dynamics can be
  modeled as a fractional diffusion process subordinate to a continuous time
  random walk. We parameterize the distribution of dwell times, hop lengths between
  dwells and correlation between hops. Next, we generalize Markov state models, treating
  the configurational states of the system as a Markov process where each state has 
  distinct transport properties. Finally apply the infinite hidden Markov model, 
  an approach capable of automatically distinguishing and parameterizing an unknown 
  number of hidden dynamical modes in multidimensional solute time series. This model
  offers a flexible approach to modeling solute motion and helps us to uncover 
  mechanisms with minimal human effort.

@@

% \LoFisShort	% use this only for 1-page Table of Figures
%\emptyLoF	% use this if there is no List of Figures

% \LoTisShort	% use this only for 1-page Table of Tables
% \emptyLoT	% use this if there is no List of Tables

### 2020-04-30 Ben_Manuscripts/thesis/transport.tex
moved things to SI

  \begin{table}[h!]
  \centering
  \begin{tabular}{ |m{3.5cm}m{1.4cm}m{2cm}|m{3.8cm}m{1.4cm}m{2cm}| }
    \hline
    \multicolumn{2}{|c}{Solute Name~~~~~~~~~Abbreviation} & Structure &\multicolumn{2}{c}{Solute Name~~~~~~~~~Abbreviation} & Structure \\
    \hline
	\color{blue}{\textbf{methanol}} & \color{blue}{\textbf{MeOH}} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/MET.pdf}
    \end{minipage} &

>>>>

  \begin{table}[h!]
  \centering
  \begin{tabular}{ |m{2.5cm}m{1.75cm}m{2cm}|m{3.8cm}m{1.4cm}m{2cm}| }
    \hline
    \multicolumn{2}{|c}{Solute Name~~~~~Abbreviation} & Structure &\multicolumn{2}{c}{Solute Name~~~~~~~~~Abbreviation} & Structure \\
    \hline
	\color{blue}{\textbf{methanol}} & \color{blue}{\textbf{MeOH}} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/MET.pdf}
    \end{minipage} &
